Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex

\textcolor{red}{Introduce each section as in the introduction of the article }

@@

\subsection*{Weighted average of partial correlation statistics}

@@

% In our experiments, we observed that the inference process is quite sensitive
% about the choice of the parameter value $\tau$ and the low-pass filter.
% Therefore, in order to reduce the variance of the results and thus the
% robustness of our approach, we perform an average over a range of parameter
% value $\tau$ from $0.100$ to $0.209$. We also perform a weighted average over
% the four low-pass filters with the following parameters
% \begin{align*}
% weight_{f_1} &= 1,\\
% weight_{f_2} &= 0.9, \\
% weight_{f_3} &= 0.7, \\
% weight_{f_4} &= 0.01
% \end{align*}
% tuned to maximize the ROC AUC on \textit{normal-1}.

\subsection*{Connectome inference from pairwise interaction statistics}

>>>>

This appendix is structured as follows: Section \ref{app:signal} describes the differences about the signal processing methods applied on fluorescent calcium time series; Section \ref{app:averaging} then provides a detailed explanation of the averaging approach; Section \ref{app:connectome} presents a heuristic trying to retrieve directivity from fluorescent calcium time series while Section \ref{app:results} finally present results validating some choices that have been made.

@@

\subsection{Weighted average of partial correlation statistics}

@@

\subsection{Connectome inference from pairwise interaction statistics}
\ref{sapp:connectome}
